Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-04-25 Manuscript/PLoSONEresponse/response.tex

Lines 308 to 309 in the previously submitted manuscript:

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
Note that this is equivalent to performing a two-sided t-test.
\end{minipage}

Lines @@@112 to @@@114 in the new manuscript:

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
Note that this is similar to performing a two-sided t-test for comparing two distribution.
\end{minipage}

\textcolor{blue}{Figure 3: B is confusing. If both curves are probability distributions, then they both have to integrate to 1. So B(y) can't cover just a subset of the area covered by B(x).}

%Fix probability distributions -> "just" distributions

\textcolor{blue}{``Combined effect of missing data parameters" section ANOVA or multiple regression are the appropriate analyses to tease apart multiple interacting factors. Here the authors opt to describe results without statistical tests, which is disappointing.}

This comment links back to the reviewer's misconception of the term ``statistics" and suspicions. ANOVA or multiple regression analysis might the appropriate analyses in some cases but we believe it isn't here. %Not comparing means, non normal distributions. ANd non-parametric version (e.g. Kruskal Wallis) not approriate either.

\textcolor{blue}{line 398: ``mMthods" -> ``Methods"}

We fixed this typo.

\textcolor{blue}{line 420: contra the statement here, a consensus collapsing to a polytomy will affect the RF distance (could go up or down, but it will change).}

%Change to "affect less" or something like that.

\textcolor{blue}{-------------------------}

\textcolor{blue}{Supplement 2:}
\textcolor{blue}{more confusion about the min RF here. Also note that if you are counting the entire leaf set as a clade (e.g the star tree having N=1), then the number of clades in rooted binary tree is n-1 (not n-2). Equation 3 has an extra ``-2" As stated it implies that the max RF distance for n=3 is 0, when the correct answer is 2.}

%check

\textcolor{blue}{The definition of the scaled RF implies that it is never positive (sinc the numerator cannot be positive and the denominator is positive).}

%check

\textcolor{blue}{The decision to use Yule trees as the base line for the mean distance is not explained, and seems odd given that the true tree are not Yule trees. I'm not sure that it makes much difference, but it is odd.}

%Because we follow Bogdanowicz and use the difference between random (NULL) trees to scale.

\textcolor{blue}{The NTS can only -infinity for distances that have the property that the mean distance between random Yule trees is 0. This is not true of either distance metric here. So the real range of values is (mean-max)/mean for both the RF and triples distance.}

%check

\textcolor{blue}{Note that JavaScript is a language, so it a bit confusing to refer to a Java program as a ``Java script."}

%fix

\textcolor{blue}{Equation (6) is not correct. You shouldn't set the summation sign as the left hand side of an equation because the notation has a standard definition. More importantly, the $\#$ of triples is the number of ways of drawing 3 (unordered) leaves from the leaf set. So it is n choose 3 not n choose 4.}

%check

\textcolor{blue}{Equation (7) is true for a three-leaf tree with a polytomy occurring with probability = 1/4 and the other 3 trees being equiprobable. I don't think that is is true for any other weighting of trees for other numbers of taxa. It might be, but the authors must show this.}

%check

\textcolor{blue}{I don't think that equations 8, 9, or 10 are correct for any case other than the 3 taxon case (though I do note that the authors are using n choose 3 here).}

%check

\textcolor{blue}{Equations 13 and 14. It seems easier to just drop the summation sign here, and just define $a_i$ and $b_i$ to the right hand side of these equations.}

%check

\textcolor{blue}{-------------------------}

\textcolor{blue}{6. If you would like your identity to be revealed to the authors, please include your name here (optional).}

\textcolor{blue}{Your name and review will not be published with the manuscript.}

\textcolor{blue}{Reviewer $\#$ 1: No thanks.}

%Fair enough!

\end{letter}
\end{document}
